### 2017-02-23 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1649 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

if(any(commandArgs()=='mdToTex')) {
# if you'll be converting md to tex, can use the following
  knitr::knit_hooks$set(plot=knitr::hook_plot_tex)  
  knitr::opts_chunk$set(
   out.width='0.45\\textwidth', 
			dev='pdf', fig.align='center')
} else {
  knitr::knit_hooks$set(plot=Pmisc::hook_plot_mdsubfig)
  knitr::opts_chunk$set(dev='png', out.width='30%')
}

@@

@lindgren2011explicit is a very good paper.

$$
f(x) = x + \int_0^\infty \exp(-\theta u^2) du
$$

@@

>>>>

if(any(commandArgs()=='mdToTex')) {
# if you'll be converting md to tex, can use the following
  knitr::knit_hooks$set(plot=knitr::hook_plot_tex)  
  knitr::opts_chunk$set(
   out.width='0.45\\textwidth', 
			dev='pdf', fig.align='center')
  mdToTex = TRUE
} else {
  knitr::knit_hooks$set(plot=Pmisc::hook_plot_mdsubfig)
  knitr::opts_chunk$set(dev='png', out.width='40%')
  mdToTex = FALSE
}

@@

@lindgren2011explicit is a very good paper, but Figure [@fig:aplot] is dull.

$$
\begin{aligned}
f(x) = &x + \int_0^\infty \exp(-\theta u^2) du\\
\rho(x) = & \sum_i x^i
\end{aligned}
$$

@@

```{r anotherplot, fig.ncol=3, fig.cap='Other uninteresting plots', fig.subcap=month.name[1:6], out.width=c('30%', '0.3\\textwidth')[1+mdToTex]}

for(D in knitr::opts_current$get()$fig.subcap) {
  hist(runif(100))
}
